---
title: "SpoonacularAPI-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}
devtools::load_all(".")
```

This SpoonacularAPI package contains functions that allow users to get information about recipes and menu items that are available on Spoonacular.

## Recipes

* `get_recipe()` gives users the names and ids of the recipes based on the parameters they entered into this function in the form of a dataframe. The description of the parameters is listed in the documentation page.

```{r}
SpoonacularAPI::get_recipe(key = Sys.getenv("SPOON_KEY"), query = "beef" ,number = 10)
```

* `get_recipe_information()` takes one or more recipe ids returned by `get_recipe()` and returns the information of the recipes in a dataframe. The output includes instructions, links to the recipes, health scores, cuisines, dish types, etc.

```{r}
SpoonacularAPI::get_recipe_information(key = Sys.getenv("SPOON_KEY"), recipe_ids = "509163,825127,600427")
```


* `get_recipe_equipment()` takes one recipe id returned by `get_recipe()` and returns the equipment required by the recipe in a dataframe.

```{r}
SpoonacularAPI::get_recipe_equipment(key = Sys.getenv("SPOON_KEY"), recipe_id = "753644")
```


* `get_recipe_ingredient()` takes one recipe id returned by `get_recipe()` and returns the ingredients required by the recipe and amount of ingredients needed in a dataframe. 

```{r}
SpoonacularAPI::get_recipe_ingredient(key = Sys.getenv("SPOON_KEY"), recipe_id = "753644")
```


* `get_recipe_nutrition()` takes one recipe id returned by `get_recipe()` and returns the basic nutritional values, bad nutrients, and good nutrients of the recipe in three dataframes. 

```{r}
SpoonacularAPI::get_recipe_nutrition(key = Sys.getenv("SPOON_KEY"), recipe_id = "753644")
```


## Menu items

* `get_menu()` gives users names and ids of the menu items based on the parameters they entered into this function in the form of a dataframe. The description of the parameters is listed in the documentation page. The output also includes the restaurant chains where the menu items are provided at.

```{r}
SpoonacularAPI::get_menu(key = Sys.getenv("SPOON_KEY"),query = "burger" ,number = 10)
```

* `get_menu_info()` takes one menu item id returned by `get_menu()` and returns the basic nutritional values of the menu item in a dataframe.

```{r}
SpoonacularAPI::get_menu_info(key = Sys.getenv("SPOON_KEY"), item_id = 419357)
```

